---
title: "Generating The Figures"
author: "Sina Aghaei"
date: "10/24/2020"
output: 
  # flexdashboard::flex_dashboard:
  #   orientation: columns
  html_document:
    # number_sections: true
 
---


In this script we provide the code for generating the figures in the paper.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE )
library(kableExtra)
library(png)
library(ggplot2)
library(reshape2)
library(egg)
require(tidyr)
require(dplyr)
library(dplyr)
library(latex2exp)
# library(ggpubr)
library(data.table)
library(RColorBrewer)
library(MASS)
require(scales)
rm(list=ls())

data_train= read.csv('./../Results/train.csv', header=TRUE, sep=',', na.strings="", stringsAsFactors =TRUE) 
data_test= read.csv('./../Results/test.csv', header=TRUE, sep=',', na.strings="", stringsAsFactors =TRUE) 

forpres=FALSE
if (forpres){
  fontfam = "sans"
} else {
  fontfam = "serif"
}

figure_path = "./"


data_train$sample <- as.factor(data_train$sample)
data_train$depth <- as.factor(data_train$depth)

data_test$sample <- as.factor(data_test$sample)
data_test$depth <- as.factor(data_test$depth)

#Let's sort the levels of approach such that the oldest method appears first
data_train$approach<- factor(data_train$approach, levels = c("OCT","BinOCT","FlowOCT","BendersOCT"))
data_test$approach<- factor(data_test$approach, levels = c("OCT","BinOCT","FlowOCT","BendersOCT"))

#Let's sort the levels of dataset with respect to their size
data_train$dataset <- factor(data_train$dataset, levels = as.character(unique(data_train[order(data_train$nrow),]$dataset)))
data_test$dataset <- factor(data_test$dataset, levels = as.character(unique(data_train[order(data_train$nrow),]$dataset)))

```


# In sample results

## Number of instances solved to optimality; No Regularization

```{r echo=TRUE, warning=FALSE}
tmp <- subset(data_train, data_train$regularization == FALSE &  data_train$status %in% c(2,101,102))

tmp <- tmp[order(tmp$solving_time),]
tmp$numOfInstances <- rowidv(tmp, cols="approach")
tmp <- tmp[,c("approach","solving_time","numOfInstances")]
names(tmp) <- c("Approach","solving_time","numOfInstances")

tmp[nrow(tmp) + 1,] = list("OCT","3600",max(subset(tmp, tmp$Approach=="OCT")$numOfInstances))
tmp[nrow(tmp) + 1,] = list("BinOCT","3600",max(subset(tmp, tmp$Approach=="BinOCT")$numOfInstances))
tmp[nrow(tmp) + 1,] = list("FlowOCT","3600",max(subset(tmp, tmp$Approach=="FlowOCT")$numOfInstances))
tmp[nrow(tmp) + 1,] = list("BendersOCT","3600",max(subset(tmp, tmp$Approach=="BendersOCT")$numOfInstances))

tmp$solving_time <- as.numeric(as.character(tmp$solving_time))
tmp$numOfInstances <- as.numeric(as.character(tmp$numOfInstances))

tmp$Approach  <- factor(tmp$Approach , levels = c("BendersOCT", "FlowOCT", "BinOCT","OCT"))
tmp <- tmp[order(tmp$Approach),]
colors <- c( brewer.pal(4, 'Set1')[3], brewer.pal(4, 'Set1')[2], brewer.pal(4, 'Set1')[4], brewer.pal(4, 'Set1')[1] ) #c("firebrick1 == 1","violetred==4","seagreen4==3","royalblue==2")
shapes <- c(15,16,17,4)
g1 <- ggplot(data = tmp, aes(x=solving_time, y=numOfInstances, group=Approach,color=Approach)) +
  geom_line(size=0.5)+ #aes(linetype=Approach)
  geom_point(aes(shape=Approach),size=2)+ 
  labs(x="Time (s)", y = "Number of Instances Solved")+
  scale_color_manual(values=colors)+
  scale_shape_manual(values=shapes)+
  theme(legend.position = "right",text = element_text(size=14,family=fontfam)) 
print(g1)

if (forpres)
{
  ggsave(paste(figure_path,"class_perf_opt_no_regularization_presentation.pdf",sep = ""),device = "pdf", width = 5, height = 3.3, units =  "in")
} else {
  ggsave(paste(figure_path,"class_perf_opt_no_regularization.pdf",sep = ""),device = "pdf", width = 5, height = 3.3, units =  "in")
}
```

We see that:
  BinOCT can solve 122 instances to optimality within 3078 seconds.
  FlowOCT can solve 141 instances to optimality within 3400 seconds.
  BendersOCT can solve 143 instances to optimality within 3500 seconds.
  OCT can solve 122 instances to optimality within 3320 seconds.
  
  OCART can solve 122 instances within 116 seconds. (3078)/116 = 26.53448 or (3600)/116 = 31.03448
  Flow can solve 122 instances within 390 seconds.  (3078)/390 = 7.892308 0r (3600)/390 =  9.23

## Number of instances solved to optimality; With Regularization

```{r echo=TRUE, warning=FALSE}
tmp <- subset(data_train, data_train$regularization == TRUE)
tmp$approach <- droplevels(tmp$approach)
tmp <- subset(tmp, tmp$status %in% c(2,101,102))
tmp <- tmp[order(tmp$solving_time),]
tmp$numOfInstances <- rowidv(tmp, cols="approach")
tmp <- tmp[,c("approach","solving_time","numOfInstances")]
names(tmp) <- c("Approach","solving_time","numOfInstances")

tmp[nrow(tmp) + 1,] = list("OCT","3600",max(subset(tmp, tmp$Approach=="OCT")$numOfInstances))
tmp[nrow(tmp) + 1,] = list("FlowOCT","3600",max(subset(tmp, tmp$Approach=="FlowOCT")$numOfInstances))
tmp[nrow(tmp) + 1,] = list("BendersOCT","3600",max(subset(tmp, tmp$Approach=="BendersOCT")$numOfInstances))

tmp$solving_time <- as.numeric(as.character(tmp$solving_time))
tmp$numOfInstances <- as.numeric(as.character(tmp$numOfInstances))

tmp$Approach  <- factor(tmp$Approach , levels = c("BendersOCT", "FlowOCT","OCT"))
tmp <- tmp[order(tmp$Approach),]

colors <- c( brewer.pal(4, 'Set1')[3], brewer.pal(4, 'Set1')[2], brewer.pal(4, 'Set1')[1], brewer.pal(4, 'Set1')[4] )
shapes <- c(15,16,4,17)
#c("firebrick1","violetred","seagreen4","royalblue")(1,3,2,4)
g2 <- ggplot(data = tmp, aes(x=solving_time, y=numOfInstances, group=Approach,color=Approach)) +
  geom_line(size=0.5)+ #aes(linetype=Approach)
  geom_point(aes(shape=Approach),size=2)+ 
  labs(x="Time (s)", y = "Number of Instances Solved")+
  scale_color_manual(values=colors)+
  scale_shape_manual(values=shapes)+
  theme(legend.position = "right", text = element_text(size=14,family=fontfam)) 
print(g2)

if (forpres)
{
  ggsave(paste(figure_path,"class_perf_opt_regularization_presentation.pdf",sep = ""),device = "pdf", width = 5, height = 3.3, units =  "in")
} else {
  ggsave(paste(figure_path,"class_perf_opt_regularization.pdf",sep = ""),device = "pdf", width = 5, height = 3.3, units =  "in")
}



```

We see that:
  FlowOCT can solve 1378 instances to optimality within 3559 seconds.
  BendersOCT can solve 1417 instances to optimality within 3449 seconds.
  OCT can solve 1078 instances to optimality within 3592 seconds.
  
  BendersOCT can solve 1078 instances within 50 seconds. (3592)/50 = 71 or (3600)/50 = 72
  Flow can solve 1078 instances within 113 seconds.  (3592)/113 = 31 or (3600)/113 = 31

