---
title: "Generating the Tables Summerizing the In Sample Results"
author: "Sina Aghaei"
date: "10/24/2020"
output: 
  # flexdashboard::flex_dashboard:
  #   orientation: columns
  html_document:
    # number_sections: true
 
---


In this script we provide the code for generating the tables summarizing the in sample results.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE )
library(kableExtra)
library(png)
library(ggplot2)
library(reshape2)
library(egg)
require(tidyr)
require(dplyr)
library(dplyr)
library(latex2exp)
# library(ggpubr)
library(data.table)
library(RColorBrewer)
library(MASS)
require(scales)
rm(list=ls())

data_train= read.csv('./../Results/train.csv', header=TRUE, sep=',', na.strings="", stringsAsFactors =TRUE) 
data_test= read.csv('./../Results/test.csv', header=TRUE, sep=',', na.strings="", stringsAsFactors =TRUE) 

forpres=FALSE
if (forpres){
  fontfam = "sans"
} else {
  fontfam = "serif"
}

figure_path = "./"


data_train$sample <- as.factor(data_train$sample)
data_train$depth <- as.factor(data_train$depth)

data_test$sample <- as.factor(data_test$sample)
data_test$depth <- as.factor(data_test$depth)

#Let's sort the levels of approach such that the oldest method appears first
data_train$approach<- factor(data_train$approach, levels = c("OCT","BinOCT","FlowOCT","BendersOCT"))
data_test$approach<- factor(data_test$approach, levels = c("OCT","BinOCT","FlowOCT","BendersOCT"))

#Let's sort the levels of dataset with respect to their size
data_train$dataset <- factor(data_train$dataset, levels = as.character(unique(data_train[order(data_train$nrow),]$dataset)))
data_test$dataset <- factor(data_test$dataset, levels = as.character(unique(data_train[order(data_train$nrow),]$dataset)))


```




```{r echo=TRUE, warning=FALSE}
find_max <- function(r){
  r <- as.character(r)
  r_mean = c()
  r_sd = c()
  final_max_score = numeric(length(r))
  for(j in r){
    r_mean = append(r_mean,unlist(strsplit(j,"$\\pm$"))[1])
    r_sd = append(r_sd,unlist(strsplit(j,"$\\pm$"))[2])
  }
  max_mean <- which(r_mean == max(r_mean))
  min_sd <- which(r_sd[max_mean] == min(r_sd[max_mean] ))
  min_sd <- max_mean[min_sd]
  
  final_max_score[max_mean] = final_max_score[max_mean] + 2
  final_max_score[min_sd] = final_max_score[min_sd] + 1
  
  max_index = which(final_max_score == max(final_max_score))
  r[max_index] <- paste("\\textbf{",r[max_index],"}",sep = "")
  
  r
}

find_min <- function(r){
  r <- as.character(r)
  r_mean = c()
  r_sd = c()
  final_max_score = numeric(length(r))
  for(j in r){
    r_mean = append(r_mean,unlist(strsplit(j,"$\\pm$"))[1])
    r_sd = append(r_sd,unlist(strsplit(j,"$\\pm$"))[2])
  }
  min_mean <- which(r_mean == min(r_mean))
  min_sd <- which(r_sd[min_mean] == min(r_sd[min_mean] ))
  min_sd <- min_mean[min_sd]
  
  final_max_score[min_mean] = final_max_score[min_mean] + 2
  final_max_score[min_sd] = final_max_score[min_sd] + 1
  
  max_index = which(final_max_score == max(final_max_score))
  r[max_index] <- paste("\\textbf{",r[max_index],"}",sep = "")
  
  r
}
```


## training acc across dataset and depth (no regularization)
```{r echo=TRUE, warning=FALSE}
# No regularization part
measure = "min"
tmp  <- subset(data_train, data_train$regularization == FALSE)

tmp <- tmp %>%
  group_by(approach,dataset,depth) %>%
  summarise(mean(gap))

names(tmp) <- c("approach","dataset","depth","metric")
tmp_wide <- dcast(melt(tmp, id.vars=c("dataset","approach","depth")), dataset + depth~ approach + variable)

if(measure == "max"){
  tmp_wide$OCT_wins <- apply(tmp_wide[,3:6],1,function(x) (x[1]==max(x))*1)
  tmp_wide$BinOCT_wins <- apply(tmp_wide[,3:6],1,function(x) (x[2]==max(x))*1)
  tmp_wide$FlowOCT_wins <- apply(tmp_wide[,3:6],1,function(x) (x[3]==max(x))*1)
  tmp_wide$BendersOCT_wins <- apply(tmp_wide[,3:6],1,function(x) (x[4]==max(x))*1)
  tmp_wide$FlowORBenders_wins <- (as.numeric(as.character(tmp_wide$FlowOCT_wins ))| as.numeric(as.character(tmp_wide$BendersOCT_wins)))*1

}else{
    tmp_wide$OCT_wins <- apply(tmp_wide[,3:6],1,function(x) (x[1]==min(x))*1)
    tmp_wide$BinOCT_wins <- apply(tmp_wide[,3:6],1,function(x) (x[2]==min(x))*1)
    tmp_wide$FlowOCT_wins <- apply(tmp_wide[,3:6],1,function(x) (x[3]==min(x))*1)
    tmp_wide$BendersOCT_wins <- apply(tmp_wide[,3:6],1,function(x) (x[4]==min(x))*1)
    tmp_wide$FlowORBenders_wins <- (as.numeric(as.character(tmp_wide$FlowOCT_wins ))| as.numeric(as.character(tmp_wide$BendersOCT_wins)))*1
}

tmp_wide$ties <- tmp_wide$OCT_wins + tmp_wide$BinOCT_wins + tmp_wide$FlowORBenders_wins
tmp_wide$flow_ties <- tmp_wide$FlowOCT_wins + tmp_wide$BendersOCT_wins 

factor_cols <- c("OCT_wins","BinOCT_wins","FlowOCT_wins","BendersOCT_wins","FlowORBenders_wins")
for(f in factor_cols){
  tmp_wide[[f]]<- as.factor(tmp_wide[[f]])
}

# print(tmp_wide[,1:6])
summary(tmp_wide[,7:11])
summary(tmp_wide[tmp_wide$ties == 1,7:11])
summary(tmp_wide[tmp_wide$ties == 1 & tmp_wide$flow_ties==1 ,7:11])
rm(tmp,tmp_wide)
```

Now let's save above tables in latex format
```{r echo=TRUE, warning=FALSE}
# No regularization part
tmp  <- subset(data_train, data_train$regularization == FALSE)

tmp <- tmp %>%
  group_by(approach,dataset,depth) %>%
  summarise(mean(train_acc),sd(train_acc),mean(gap),sd(gap),mean(solving_time),sd(solving_time))

names(tmp) <- c("approach","dataset","depth","acc_mean","acc_sd","gap_mean","gap_sd","time_mean","time_sd")

tmp$acc <- paste(format(round(tmp$acc_mean, 2), nsmall = 2),"$\\pm$",sep = "")
tmp$acc <- paste(tmp$acc,format(round(tmp$acc_sd, 2), nsmall = 2),sep = "")
tmp$acc_mean <- NULL
tmp$acc_sd <- NULL

tmp$gap <- paste(format(round(tmp$gap_mean, 2), nsmall = 2),"$\\pm$",sep = "")
tmp$gap <- paste(tmp$gap,format(round(tmp$gap_sd, 2), nsmall = 2),sep = "")
tmp$gap_mean <- NULL
tmp$gap_sd <- NULL

tmp$time <- paste(format(round(tmp$time_mean, 0), nsmall = 0),"$\\pm$",sep = "")
tmp$time <- paste(tmp$time,format(round(tmp$time_sd, 0), nsmall = 0),sep = "")
tmp$time_mean <- NULL
tmp$time_sd <- NULL

tmp_wide <- dcast(melt(tmp, id.vars=c("dataset","approach","depth")), dataset + depth~ approach + variable)

for(i in 1:nrow(tmp_wide)){
  tmp_wide[i,seq(3,14,3)] <- find_max(tmp_wide[i,seq(3,14,3)])
  tmp_wide[i,seq(4,14,3)] <- find_min(tmp_wide[i,seq(4,14,3)])
  tmp_wide[i,seq(5,14,3)] <- find_min(tmp_wide[i,seq(5,14,3)])
}

print(tmp_wide)
write.table(tmp_wide, "in_sample_reg.txt",row.names = FALSE,sep = "&",eol = "\\\\", quote=FALSE)
```


## training acc across dataset and depth (with regularization)

Since the comparison of training acc over different values of lambdas does not make sense, we exclude training_acc from this table.

```{r echo=TRUE, warning=FALSE}
# No regularization part
measure = "min"
tmp  <- subset(data_train, data_train$regularization == TRUE)

tmp <- tmp %>%
  group_by(approach,dataset,depth) %>%
  summarise(mean(solving_time))

names(tmp) <- c("approach","dataset","depth","metric")
tmp_wide <- dcast(melt(tmp, id.vars=c("dataset","approach","depth")), dataset + depth~ approach + variable)

if(measure == "max"){
  tmp_wide$OCT_wins <- apply(tmp_wide[,3:5],1,function(x) (x[1]==max(x))*1)
  tmp_wide$FlowOCT_wins <- apply(tmp_wide[,3:5],1,function(x) (x[2]==max(x))*1)
  tmp_wide$BendersOCT_wins <- apply(tmp_wide[,3:5],1,function(x) (x[3]==max(x))*1)
  tmp_wide$FlowORBenders_wins <- (as.numeric(as.character(tmp_wide$FlowOCT_wins ))| as.numeric(as.character(tmp_wide$BendersOCT_wins)))*1

}else{
    tmp_wide$OCT_wins <- apply(tmp_wide[,3:5],1,function(x) (x[1]==min(x))*1)
    tmp_wide$FlowOCT_wins <- apply(tmp_wide[,3:5],1,function(x) (x[2]==min(x))*1)
    tmp_wide$BendersOCT_wins <- apply(tmp_wide[,3:5],1,function(x) (x[3]==min(x))*1)
    tmp_wide$FlowORBenders_wins <- (as.numeric(as.character(tmp_wide$FlowOCT_wins ))| as.numeric(as.character(tmp_wide$BendersOCT_wins)))*1
}

tmp_wide$ties <- tmp_wide$OCT_wins + tmp_wide$FlowORBenders_wins
tmp_wide$flow_ties <- tmp_wide$FlowOCT_wins + tmp_wide$BendersOCT_wins 


factor_cols <- c("OCT_wins","FlowOCT_wins","BendersOCT_wins","FlowORBenders_wins")
for(f in factor_cols){
  tmp_wide[[f]]<- as.factor(tmp_wide[[f]])
}

# print(tmp_wide[,1:5])
summary(tmp_wide[,6:9])
summary(tmp_wide[tmp_wide$ties == 1,6:9])
summary(tmp_wide[tmp_wide$ties == 1 & tmp_wide$flow_ties==1 ,6:9])
rm(tmp,tmp_wide)
```

Now let's save the above table in a latex table format
```{r echo=TRUE, warning=FALSE}
# No regularization part
tmp  <- subset(data_train, data_train$regularization == TRUE)

tmp <- tmp %>%
  group_by(approach,dataset,depth) %>%
  summarise(mean(gap),sd(gap),mean(solving_time),sd(solving_time))

names(tmp) <- c("approach","dataset","depth","gap_mean","gap_sd","time_mean","time_sd")


tmp$gap <- paste(format(round(tmp$gap_mean, 2), nsmall = 2),"$\\pm$",sep = "")
tmp$gap <- paste(tmp$gap,format(round(tmp$gap_sd, 2), nsmall = 2),sep = "")
tmp$gap_mean <- NULL
tmp$gap_sd <- NULL

tmp$time <- paste(format(round(tmp$time_mean, 0), nsmall = 0),"$\\pm$",sep = "")
tmp$time <- paste(tmp$time,format(round(tmp$time_sd, 0), nsmall = 0),sep = "")
tmp$time_mean <- NULL
tmp$time_sd <- NULL

tmp_wide <- dcast(melt(tmp, id.vars=c("dataset","approach","depth")), dataset + depth~ approach + variable)

for(i in 1:nrow(tmp_wide)){
  tmp_wide[i,seq(3,8,2)] <- find_min(tmp_wide[i,seq(3,8,2)])
  tmp_wide[i,seq(4,8,2)] <- find_min(tmp_wide[i,seq(4,8,2)])
}

write.table(tmp_wide, "in_sample_no_reg.txt",row.names = FALSE,sep = "&",eol = "\\\\", quote=FALSE)
```
